---
title: "RWorksheet_cadiz#4c"
author: "John Dave R. Cadiz"
date: "2024-11-03"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Use the dataset mpg

## a. Show your solutions on hpw to import a csv file into the environment
```{r}
library(ggplot2)

mpgdata <- read.csv("mpg.csv")
str(mpgdata)
```
## b. Which varialbles from mpg data are categorical?
```{r}
# The categorical variables from the mpg data set are manufacture, model, year,
# cyl, trans, drv, fl, and class.
```
## c. Which are continouse variables?
```{r}
# The continious variable from the data set mpr are displ, cty, and hwy.
```

## 2. Which manufacturer has the most models in this data set? Which model has
## has the most variations? Show your answer?

## a. Group the manufacturers and find the unique model. Show your codes and 
##result.
```{r}
library(dplyr)
manufacturer_model <- mpg %>%
  group_by(manufacturer) %>%
  summarize(model_num = n_distinct(model)) %>%
  arrange(desc(model_num))

manufacturer_model

variations_num <- table(mpg$model)
variations_num [variations_num == max(variations_num)]
```
## b. Graph the result by using plot() and ggplot(). Write the codes and its 
## result.
```{r}
manufacturer_data <- setNames(
  manufacturer_model$model_num, 
  manufacturer_model$manufacturer
  )

barplot(manufacturer_data, 
        main = "Number of Models per Manufacturer",
        xlab = "Manufacturer",
        ylab = "Number of Models",
        col = c("pink", "purple", "skyblue", "grey", "orchid"),
        las = 3)

variations_num <- mpg %>%
  group_by(model) %>%
  summarize(count = n()) %>%
  arrange(desc(count))

variations_num

ggplot(variations_num,
       aes(x = reorder(model, -count), y = count)) +
       geom_bar(stat = "identity", fill = "pink") +
       labs(title = "Number of Variations per Model", x = "Model", y = "Count") +
       theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
## 2. Same dataset will be used. You are going to show the relationship between 
##the model and the manufacturer.

## a. What does ggplot(mpg,aes(model, manufacturer)) + geom_point() show?
```{r}
ggplot(mpg,aes(model, manufacturer)) + geom_point()

# this snippet shows the code of a scatter plot by two data named models and 
#manufacturers.
```
## b. For you, is it useful? If not, how could you modify the data to make it 
##more informative?
```{r}
# For me, it could be better to not use the scatter plot in this type of 
#visualization because it is difficult to track and interpret the given data. 
#I will modify it and change to bar graph, by this I could show the difference 
#between each models and manufacturer by using the labels and specific colors 
#in this way it can help me to track and interpret the data without error.
```
## 3.Plot the mdoel and the year using ggplot(). Use only the top 20
##observations. Write the codes and its results.
```{r}
topobservation <- mpg[1:20, ]

ggplot(topobservation, 
       aes(x = model, y = year)) +
       geom_point(color = "purple", size = 2) +
       labs(
          title = "Model and Year (Top 20 Observations)",
          x = "Model",
          y = "Year") +
       theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
## 4. Using the pipe (%>%), group the model and get the number of cars per 
##model. Show codes and its result.
```{r}
library(dplyr)

carcountpermodel <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n())

print(carcountpermodel)
```

## a. Plot using geom_bar() using the top 20 observation only. 
##The graphs should have title, labels and colors. show code and its results.
```{r}

ggplot(top_20_models, aes(x = reorder(model, -car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  labs(
    title = "Top 20 Car Models by Number of Cars",
    x = "Car Model",
    y = "Number of Cars"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1), 
    legend.position = "none" 
  ) +
  scale_fill_manual(values = colorRampPalette(c("#D8BFD8", "#800080"))(20)) 

```
## b. Plot using the geom_bar() + coord flip() just like what is shown below. 
##Show codes and its result.
```{r}
library(dplyr)
library(ggplot2)

top_20_models <- carcountpermodel %>%
  arrange(desc(car_count)) %>%
  head(20)

ggplot(top_20_models, aes(x = reorder(model, car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +  
  labs(
    title = "Top 20 Car Models by Number of Cars",
    x = "Car Model",
    y = "Number of Cars"
  ) +
  theme_minimal() +
  theme(legend.position = "none") +  
scale_fill_manual(values = colorRampPalette(c("#D8BFD8", "#800080"))(20))
```

## 5. Plot the relationship between cyl - number of cylinders and disply - 
##engine displacement using geom_point with aesthetic color = engine
##displacement. Title should be "Relationship between No. of Cylinders 
##and Engine Displacement".

## a. How would you describe its relationship? Show the code and its result.
```{r}
library(ggplot2)

ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point() +
  labs(
    title = "Relationship between No. of Cylinders and Engine Displacement",
    x = "Number of Cylinders",
    y = "Engine Displacement"
  ) +
  scale_color_gradient(low = "lightblue", high = "darkblue") + 
  theme_minimal()

# It shows that as the number of cylinders increases, engine displacement also 
#increases, indicating a positive relationship. However, variability exist 
#within each cylinder group, and the relationship is not perfectly linear due 
#to the differences in engine design and vehicle type.
```

## 6. Plot the relationship between displ (engine displacement) and hwy 
##( highway miles per gallon). Mapped it with a continous variable you have 
##identified in #1-c. What is its result? Why it produced such output?
```{r}
library(ggplot2)

ggplot(mpg, aes(x = displ, y = hwy, color = cty)) +
  geom_point() +
  labs(
    title = "Relationship between Engine Displacement and Highway MPG",
    x = "Engine Displacement",
    y = "Highway Miles per Gallon",
    color = "City MPG"
  ) +
  scale_color_gradient(low = "lightgreen", high = "orange") + 
  theme_minimal()

## To answer it, the plot reveals the negative relationship between engine 
##displacement(displ) and highway mpg(hwy), with larger engines generally 
##achieving lower highway mileage. in addition, cars with lower city MPG(cty) 
##tend to have large displacements, as these engines consumes more fuel, 
##leading to lower fuel efficiency overall.
```

## 6. Import the traffic.csv onto your R environment.
```{r}
trafficdata <- read.csv("traffic.csv")
```


## a. How many numbers of observation does it have? What are the variables of 
## the traffic datasets the Show your answer.
```{r}
numberof_observation <- nrow(trafficdata)
variables <- colnames(trafficdata)

cat("Number of observations:", numberof_observation, "\n")
cat("Variables:", variables, "\n")

```
## b.Subset the dataet into the junctions. What is the R code and its output.
```{r}
junctionslist <- split(trafficdata, trafficdata$Junction)

lapply(junctionslist, head)
```
## c. Plot each junction in a geom_line(). Show your solution and output.
```{r}
library(dplyr)
library(ggplot2)

trafficdata$DateTime <- as.Date(trafficdata$DateTime, format = "%Y-%m-%d")

ggplot(trafficdata, aes(x = DateTime, y = Vehicles, color = Junction)) +
  geom_line() +
  labs(
    title = "Traffic Volume Over Time by Junction",
    x = "Date",
    y = "Vehicle Count"
  ) +
  theme_minimal() +
  facet_wrap(~ Junction, scales = "free_y") +  
  theme(legend.position = "none")              
```

## 7. From the alexa_file.xlsx, import it to your environment.


## a. How many observation does alexa_file has? What about the number of columns? Show your solution and answer.

## b. group the variations and get the total of each variations. Use dplyr package. Show solution and answer.

## c. Plot the variations using the ggplot() function. What did you observed? Complete the details of the graph. Show solution and answer.

## d. Plot a geom_line() with the date and the number of verified reviews. Complete the details of the graphs. Show your answer and solution.

## e. Get the relationship of variations and ratings. Which variations got the most highest rating? Plot a graph to show its relationship. Show your solution and answer.
