---
title: "Rworksheet_cadiz#2"
author: "John Dave R. Cadiz"
date: "2024-09-23"
output: html_document

**fff** 1. Create a vector using : operator
```{r}
# a. Sequence from -5 to 5. Write the R code and its output. Describe its output.
sequence <- -5:5
print(sequence)

# The output of this code is from negative five to positive five.

# b. x <- 1:7. What will be the value of x?
x <- 1:7
print(x)
# The value of x are numbers from one to seven.

```
**fff** 2. Create a vector using seq() function
```{r}
# a. seq(1, 3, by = 0.2) # specify step size
# Write the R Script and its output. Describe the output.

sql <- seq(1, 3, by = 0.2)
print(sql)
# The output of this script are the number from 1 going to 3 how ever there is changes from the incrementation instead of increment in one, the incrementation is 0.2 every number.
```
**fff** 3. A factory has a census of its workers. There are 50 workers in total. The following list shows their ages: 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18.
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

# a. Access the 3rd element, what is the value
ages[3]
# The value of the third element of ages is 22.

# b. Access 2nd and 4th element, what are the values?
ages[c(2,4)]
# The value of second and fourht elements are 28 and 36.

# c. Access all but the 4th and 12 element is not included. Write the R script and its output.
ages[-c(4, 12)]

```
**fff** 4. Create a vector x <- c("First" = 3, "second" = 0, "third" = 9). Then named the vector, names(x).
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)

# a. Print the results. Then access x[c("first", "third)] Describe the output.
print(x)

x[c("first", "third")]

# The output of the accessed x[c("first", "third)] are 3 and 9.

# b. Write the code and its output.
x <- c("first" = 3, "second" = 0, "third" = 9)
print(x)
```
**fff** 5. Create a sequence x from -3:2.
```{r}

x <- -3:2
# a. Modify 2nd element and change it to 0;
  x[2] <- 0
  print(x)
  
  #Describe the output.
  # The output is range from negative three to positive 2 how ever the second element turns to zero because it change the value to 0.

# b. Write the code and its output.
x <- -3:2
print(x)
```

**fff** 6. The following data shows the diesel fuel purcse by Mr. Cruz.
```{r}
# a. Create a data drame for month, price per liter (php) and purchase-quantity (liter). Write the R scripts and its output.

fuel_data <- data.frame(Month = c("Jan", "Feb", "March", "Apr", "May", "June"), Price_per_Liter_Php =  c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00), Purchaseq = c(25, 30, 40, 50, 10, 45))

print(fuel_data)
```

```{r}
# b. What is the average fuel expenditure of Mr. Cruz from Jan to June? Note: Use 'weighted.mean(liter, purchase)'. Write the R scripts and its output.
Price_per_Liter_Php <- c(52.50, 57.25, 60.00, 65.00)
Purchaseq <- c(25, 30, 50, 40)

average_expenditure <- weighted.mean(Price_per_Liter_Php, Purchaseq)

print(average_expenditure)
```

**fff** 7. R has actually lots of built-in datasets. For example, the rives data "gives the lengths (in miles) of 141 "major" rivers in North America, as compiled by the US Geological Survey".
```{r}
# a. Type "rivers: in R console. Create a vector data with 7 elements, containing the number of elements (length) in rivers, their sum (sum), mean (mean), median (median), variance (var), standard deviation (sd), minumum (min) and maximum (max).

data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))

print(data)

# b. What are the results?
# The results shows that 141.0000  83357.0000    591.1844    425.0000 243908.4086    493.8708    135.0000   3710.0000

# c. Write the R scripts and its outputs.
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))

print(data)
```
**fff** 8. The table below gives the 25 most powerful celebrities and their annual pay as ranked by the editions of Forbes magazine and as listed on the Forbes.com website.
```{r}
#. a. Create vectors according to the above table. Write the R Scripts and its output.

power_ranking <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25)

celebrity_name <- c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg", "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen", "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", "David Letterman", "Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson", "Dr. Phil McGraw", "Jay Leno", "Celine Dion", "Kobe Bryant")

pay <- c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 25, 39, 45, 32, 40, 31)

print(power_ranking)
print(celebrity_name)
print(pay)

```
```{r}
 # b. Modify the power ranking and pay of J.K. Rowling. Changes power ranking to 15 and pay to 90. Write the R scripts and its output.
index_jk <- which(celebrity_name == "J.K Rowling")

power_ranking <- power_ranking[-index_jk]
celebrity_name <- celebrity_name[-index_jk]
pay <- pay[-index_jk]

power_ranking <- append(power_ranking, 15, after = 14)
celebrity_name <- append(celebrity_name, "J.K Rowling", after = 14)
pay <- append(pay, 90, after = 14)

print(power_ranking)
print(celebrity_name)
print(pay)
```
```{r}
# c. Create an excel file from the table above and save it as csv file(PowerRanking). Import the cvs file into the RStudio. What is the R script?
data <- read.csv("Power Ranking.csv")
print(data)



# d. Access the rows 10 to 20 and save it as Ranks.RData. Write the R scripts and its output.
anotherdata <- data[10:20, ]
save(anotherdata, file = "Rank.Rdata")
print(anotherdata)

```
```{r}
# e. Describe its output. 
# The output of the letter d are the following row from 10 to 20. It contains the rankings, name of the celebrities, and their pays.
```

```

**fff** 9. Download the Hotels-Vienna https://tinyurl.com/Hotels-Vienna
```{r}

# a. Import the excel file into your RStudio. What is the R script?
library(openxlsx)
d <- read.xlsx("/cloud/project/Lab_Activities/hv.xlsx")
  
```

```{r}
# b. How many dimensions does the dataset have? What is the R script? What is its output?
dimes <- dim(d)
print(dimes)
```
```{r}
# c. Select columns country, neighbourhood, priceSelect columns country, neighbourhood, price, stars, accomodation_type, and ratings. Write the R script.

selcol <- d[, c("country", "neighbourhood","price", "stars", "accommodation_type", "rating")]
```

```{r}
# d. Save the data as new.RData to your RStudio. Write the R script

save(selcol, file = "new.RData")
```

```{r}
# e. Display the first six rows and last six rows of the new.RData. What is the R script?


head(selcol)
tail(selcol)
```

**fff** 10. Create a list of ten (10) vegetables you ate during your lifeline. If none, just list down.
```{r}
# a. Write the R scripts and its output.
vegetables <- list("cabbage", "lettuce", "peanuts", "onion", "garlic", "broccoli", "carrot", "potato", "spinach", "egg plant")

print(vegetables)

# b. Add 2 additional vegetables after the last vegetables in the list. What is the R scripts and its output?
vegetables <- c(vegetables, list("sweet potato", "cauliflower"))

print(vegetables)

# c. Add 4 additional vegetables after index 5. How many datapoints does your vegetables list have? What is the R script and its output?
vegetables <- c(vegetables, list("peas", "ube", "cucumber", "beans"))

print(vegetables)
# d. Remove the vegetables in index 5, 10, and 15. How many vegetables were left? Write the codes and its output.
vegetables <- vegetables[-c(5, 10, 15)]

print(vegetables)
```

