---
title: "Rworksheet_cadiz#4a"
author: "John Dave R. Cadiz"
date: "2024-10-21"
output: pdf_document
---


```{r}
## 1. The table below shows the data about shoe size and height. Create a data frame.
shoesize <- c(6.5, 9.0, 8.5, 8.5, 7.0, 9.0, 9.5, 13.0, 7.5, 10.5, 10.5, 12.0, 10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 11.0, 9.0, 13.0)

height <- c(66.0, 68.0, 65.0, 65.0, 64.0, 71.0, 72.0, 72.0, 74.5, 67.0, 74.5, 71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0, 69.0, 72.0, 70.0, 69.0, 70.0)

gender <- c("F", "F", "F", "F", "F", "F", "F", "M", "F", "M", "M", "M", "M", "M", "M", "F", "F", "M", "F", "F", "F", "M", "F", "M", "M", "M", "M")

shoedata <- data.frame(ShoeSize = shoesize, Height = height, Gender = gender)

print(shoedata)

```
## a. Describe the data.
```{r}
#Data frame shoedata are the data frome the table above it shows the record of the size, height, and gender of the user.
```
## b. Create a subset by males and females with their corresponding shoe size and heigth. What its result? Show the R Scripts.
```{r}
maledata <- subset(shoedata, Gender == "M", select = c(ShoeSize, Height))

print(maledata)

femaledata <- subset(shoedata, Gender == "F", select = c(ShoeSize, Height))

print(femaledata)
```
## c. Find the mean of the shoe size and the height of the respondents. Write the R scripts and its results.
```{r}
mean_shoesize <- mean(shoedata$ShoeSize)
print(mean_shoesize)

mean_height <- mean(shoedata$Height)
print(mean_height)
```
## d. Is there a relationship between shoe size and height? Why?
```{r}
# Yes, because as shown as the table above as the height increase the shoe size also increase, this could be a factor of increasing shoe size because of height of the respondent.
```


## 2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R scripts print out the factor levels below the actual values.

## Consider data consisting of the names of months: "March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "Janiary", "November", "November", "February", "May", "August", "July", "December", "August", "August", "August", "September", "November", "February", "April")
```{r}
months_vector <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "November", "November", "February", "May", "August", "July", "December", "August", "August", "August", "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)

print(factor_months_vector)
```
## 3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results if both vectors. Are they both equally useful in this case?
```{r}
summary_monthsvector <- summary(months_vector)
print(summary_monthsvector)

summary_factormonthsvector <- summary(factor_months_vector)
print(summary_factormonthsvector)


## It shows the result of the object, summary tells the length, class, and mode of the number of characters. In line with this its states the number of months mentioned, in this way it is useful to use this r code so that it sorts automatically and gives information regarding to the number of months tallied from the data above.
```
## 4. Create a vector and factor for the table below.
```{r}
Direction <- c("East", "West", "North", "West", "North", "West", "North", "West")

factor_data<- factor(Direction)

new_order_data <- factor(factor_data, levels = c("East", "West", "North"))

print(new_order_data)
```

## 5. Enter the data below in Excel with file name= import_march.csv 

## a. Import the excel file into the Environment Pane using read.table() function. Write the code.
```{r}
dataexcel<- read.table("import_march.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
```
## b. View the dataset. Write the R scripts and its results.
```{r}
print(dataexcel)
```
## 6. Full Search

# Exhaustive search is a methodology for finding an answer by exploring all possible cases.
