---
title: "Rworksheet_cadiz#4a"
author: "John Dave R. Cadiz"
date: "2024-10-21"
output: pdf_document
---


```{r}
## 1. The table below shows the data about shoe size and height. Create a data frame.
shoesize <- c(6.5, 9.0, 8.5, 8.5, 7.0, 9.0, 9.5, 13.0, 7.5, 10.5, 10.5, 12.0, 
              10.5, 13.0, 11.5, 8.5, 5.0, 10.0, 6.5, 7.5, 8.5, 10.5, 8.5, 10.5, 
              11.0, 9.0, 13.0)

height <- c(66.0, 68.0, 65.0, 65.0, 64.0, 71.0, 72.0, 72.0, 74.5, 67.0, 74.5, 
            71.0, 71.0, 77.0, 72.0, 59.0, 62.0, 72.0, 66.0, 64.0, 67.0, 73.0,
            69.0, 72.0, 70.0, 69.0, 70.0)

gender <- c("F", "F", "F", "F", "F", "F", "F", "M", "F", "M", "M", "M", "M", 
            "M", "M", "F", "F", "M", "F", "F", "F", "M", "F", "M", "M", "M", "M")

shoedata <- data.frame(ShoeSize = shoesize, Height = height, Gender = gender)

print(shoedata)

```
## a. Describe the data.
```{r}
#Data frame shoedata are the data frome the table above it shows the record of
#the size, height, and gender of the user.
```
## b. Create a subset by males and females with their corresponding shoe size 
##and height. What its result? Show the R Scripts.
```{r}
maledata <- subset(shoedata, Gender == "M", select = c(ShoeSize, Height))

print(maledata)

femaledata <- subset(shoedata, Gender == "F", select = c(ShoeSize, Height))

print(femaledata)
```
## c. Find the mean of the shoe size and the height of the respondents.
##Write the R scripts and its results.
```{r}
mean_shoesize <- mean(shoedata$ShoeSize)
print(mean_shoesize)

mean_height <- mean(shoedata$Height)
print(mean_height)
```
## d. Is there a relationship between shoe size and height? Why?
```{r}
# Yes, because as shown as the table above as the height increase the shoe size 
#also increase, this could be a factor of increasing shoe size 
#because of height of the respondent.
```


## 2. Construct character vector months to a factor with factor() and assign the
##result to factor_months_vector. Print out factor_months_vector and 
##assert that R scripts print out the factor levels below the actual values.

## Consider data consisting of the names of months: "March", "April", "January",
##"November", "January", "September", "October", "September", "November", 
##"August", "Janiary", "November", "November", "February", "May", "August", 
##"July", "December", "August", "August", "August", "September", "November", 
##"February", "April")
```{r}
months_vector <- c("March", "April", "January", "November", "January", 
                   "September", "October", "September", "November", "August", 
                   "January", "November", "November", "February", "May", 
                   "August", "July", "December", "August", "August", "August", 
                   "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)

print(factor_months_vector)
```
## 3. Then check the summary() of the months_vector and factor_months_vector. 
##Interpret the results if both vectors. 
##Are they both equally useful in this case?
```{r}
summary_monthsvector <- summary(months_vector)
print(summary_monthsvector)

summary_factormonthsvector <- summary(factor_months_vector)
print(summary_factormonthsvector)


## It shows the result of the object, summary tells the length, class, and mode 
##of the number of characters. In line with this its states the number of months
##mentioned, in this way it is useful to use this r code so that it sorts 
##automatically and gives information regarding to the number of months tallied 
##from the data above.
```
## 4. Create a vector and factor for the table below.
```{r}
Direction <- c("East", "West", "North", "West", "North", "West", "North", "West")

factor_data<- factor(Direction)

new_order_data <- factor(factor_data, levels = c("East", "West", "North"))

print(new_order_data)
```

## 5. Enter the data below in Excel with file name= import_march.csv 

## a. Import the excel file into the Environment Pane using read.table() 
##function. Write the code.
```{r}
dataexcel<- read.table("import_march.csv", header = TRUE, sep = ",", 
                       stringsAsFactors = FALSE)
```
## b. View the dataset. Write the R scripts and its results.
```{r}
print(dataexcel)
```
## 6. Full Search

## Exhaustive search is a methodology for finding an answer by exploring 
##all possible cases.

## When tring to find a desired number in a set of given numbers, the method of 
##finding the corresponding number by checkug all elements in the set one by one 
##can called an exhaustive search. Implement an exhaustive search function that 
##meets the input/output conditions below.

## a. Create an R Program that allows the user to randomly select numbers 
##from 1 to 50. Then display the chosen number. If the number is beyond the range 
##of the selected choice, it will have to displat a string "The number selected is 
##beyond the ranfe of 1 to 50". If the number is inputted by the user, 
##it will have to display "TRUE", otherwise display the input number.
```{r}
exhaustives <- function() {
 
  selected_number <- as.numeric(readline(prompt = "Select a number from 1 to 50: "))
  
if (selected_number < 1 || selected_number > 50) {
    print("The selected number is beyond the range of 1 to 50") 
  } else if (selected_number == 20) {
    print("TRUE")
  } else {
    print(selected_number)
  }
}
```

## 7. Change

##At ISATU Univesity's traditional cafeteria, snacks can only be purchased with
##bills. A long-standing rule at the concession standt is that snacks must be 
##purchased with as few coins as possible. There are three types of bills: 
## 50 pesos, 100 pesos, 200 pesos, 500 pesos, and 1000 pesos.

## a. Write a function that prints the minimum number of bills that must be 
##paid, given the price of the snanck.

## Input: Price of snack ( a random number divisible by 50) 
##Output: Minimum number of bills needed to purchase a snack
```{r}
min_bills <- function(price) {
  bills <- c(1000, 500, 200, 100, 50)
  
  num_bills <- 0
  for(bill in bills) {
    count <- price %/% bill
    num_bills <- num_bills + count
    
    price <- price %% bill
  }
  
  print(paste("Minimum number of bills needed to purchase a snack: ", num_bills))
}

min_bills(1250)
```
## 8. The following is each student's math score for one semester. 
##Based on this, answer the following questions.


## a. Create a data frame from the above table. Write the R codes and its output.
```{r}
name <- c("Annie", "Thea", "Steve", "Hanna")
grade1 <- c(85, 65, 75, 95)
grade2 <- c(65, 75, 55, 75)
grade3<- c(85, 90, 80, 100)
grade4 <- c(100, 90, 85, 90)

gradesdf <- data.frame( 
  Name = name, Grade_1 = grade1, Grade_2= grade2, Grade_3 = grade3, 
  Grade_4 = grade4)

print(gradesdf)

```
## b. Without using the rowMean function, output the average score of studens 
##whose average math score over 90 points during the semester. 
##Write the R code and its output.

# Example Output: Annie's Average grade this semester is 88.75.
```{r}
gradesdf$Average <- (gradesdf$Grade_1 + gradesdf$Grade_2 + gradesdf$Grade_3 + 
                       gradesdf$Grade_4) / 4


for (i in 1:nrow(gradesdf)) {
  if (gradesdf$Average[i] > 90) {
    cat(gradesdf$Name[i], "'s Average grade this semester is", 
        round(gradesdf$Average[i], 2), ".\n")
  }
}
```
## c. Without using the mean functuon, output as follows for the tests in which
##the average score was less than 80 out of 4 tests.

# Example output: The nth test was difficult.

```{r}
for (j in 2:5) { 
  total_test_score <- sum(gradesdf[, j])
  avg_test_score <- total_test_score / nrow(gradesdf)
  
  if (avg_test_score < 80) {
    test_num <- j - 1
    print(paste("The", test_num, 
            ifelse(test_num == 1, "st", 
            ifelse(test_num == 2, "nd", 
            ifelse(test_num == 3, "rd", "th"))), "test was difficult."))
  }
}
```
## d. Without using the max function, output as follows for students whose 
##highest score gor a semester exceeds 90 points.

# Example output: Annie's highest grade this semester is 95.
```{r}
for (i in 1:nrow(gradesdf)) {

  grades <- c(gradesdf$Grade_1[i], gradesdf$Grade_2[i], gradesdf$Grade_3[i], 
              gradesdf$Grade_4[i])

  highest_grade <- grades[1]

  for (grade in grades) {
    if (grade > highest_grade) {
      highest_grade <- grade
    }
  }

  if (highest_grade > 90) {
    print(paste(gradesdf$Name[i], "'s highest grade this semester is", 
                highest_grade))
  }
}
```

