---
title: "Rworksheet_cadiz#1"
author: "John Dave R. Cadiz"
date: "2024-09-04"
output: pdf_document
---
## 1. Set up a vector named age, consisting of 34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41.
```{r}

age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 
         37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
```

## a. How many data points?
```{r}
length (age)
```

## b. Write the R code and its output
```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 
         46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41)
print(age)
```

## 2. Find the reciprocal of the value for age.
```{r}
reciprocal <- 1 / age
library("MASS")
fractions(reciprocal)
```

## Write the R code and its output
age <- 1/age
```{r}
reciprocal <-1 / age
library("MASS")
fractions(reciprocal)
```

## 3. Assign also new_age <- c(age, 0, age)
```{r}
new_age <- c(age,0,age)
print(new_age)
```

## What happen to the new_age?
 - It happened that the new printed age is has a 0 separator and prints the value which explains the code of vector c(age,0,age)


## 4. Sort thge values of age.
#Write the R code and its output.
```{r}
sort(age)
```

## 5. Find the minimum and maximum value for age.

## Write the R code for minimum
```{r}
min(age)
```

## Write the R code for maximum
```{r}
max(age)
```
## 6. Set up a vector named data, consisting of 2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5,2.3, 2.4, and 2.7
```{r}
data1 <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```

## a. How many data points
```{r}
length(data)
```

## b. Write the R code and its output
```{r}
data1 <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5, 2.3, 2.5, 2.3, 2.4, 2.7)
```

## 7. Generates a new vector for data where you double every value of the data. | What happen to the data?
```{r}
data1 <- data1 * 2
print(data1)
```
## 8. Generate a sequence for the following senario: 

## 8.1 Integers from 1 to 100.
```{r}
int <- seq(1,100)
print(int)
```
## 8.2 Numbers from 20 to 60
```{r}
squence <- seq(20,60)
print(squence)
```
## 8.3 Mean of numbers from 20 to 60
```{r}
  mean(20:60)
```
## 8.4 Sum of numbers from 51 to 91
```{r}
  sum(51:91)
```
## 8.5 Integers from 1 to 1,000
```{r}
  thousand <- seq(1:1000)
  print(thousand)
```
## a. How many data points from 8.1 to 8.4?
 - 103 data points

## b. Write the R code and its output from 8.1 to 8.4.
```{r}
length(int) + length(sequence) + length(mean) + length(sum)
```

## c. For 8.5 find only maximum data points until 10.
```{r}
max(thousand[thousand <- 10])
```


## 9. Print a vector with the integers between 1 to 100 that are not divisible by 3, 5, and 7 using filter option.

- Filter(function(i) { all(i%% c C3,5,7) !=0}, seq(100))

## Write the R code and its output.
```{r}
number <- seq(1:100)

result <- Filter(function(i) { all(i %% c(3,5,7) != 0) }, number)

print(result)
```
## 10. Generate a sequence backwards of the integers from 1 to 100.

## Write the R code and its output.
```{r}
  reverse <- seq(100,1)
  print(reverse)
```
## 11. List all the natural number below 25 that are multiples of 3 or 5.
```{r}
multiples <- c()

for (i in 1:24) {
  if (i %% 3 == 0 || i %% 5 == 0) {
    multiples <- c(multiples, i)
  }
}
print(multiples)
```


## Find the sum of these multiples.
```{r}
sum(multiples)
```

## a. How many data points from 10 to 11?
```{r}
length(reverse) + length(multiples) + length(sum)
```


## b. Write the R code and its output from 10 and 11.

## 12. Statements can be grouped together using braces '{' and '}'. A group statements is sometimes called a block. Single statements are evaluated when a new line is typed at the end of the syntactically complete statement. Blocks are not evaluated until a new line is entered after the closing brace.

## Enter this statement:
  x <- {0 + x  + 5 +}
```{r}
  #x <- {0 + x + 5 +}
```

## Describe the output:
  - The results stated that there is an error due to incomplete expression, in order to void the code i turned the expression into comment.


## 13. Set up a vector named score, consisting of 72, 86, 92, 63, 88, 91, 92, 75, 75, and 77. To access individual elements of an atomic vector, one generally uses the x[i] construction.
- Find x[2] and x[3]. Write the R code and its output.

```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)

score[2]
score[3]
```
## 14. Create a vector a = c(1, 2, NA, 4, NA, 6, 7)

## A. Change the NA to 999 using codes print(a,na.print="-999")
```{r}
 a = c(1, 2, NA, 4, NA, 6, 7)

print(a, na.print="-999")
```
## b. Write the R code and its out. Describe the output.
```{r}
  a = c(1, 2, NA, 4, NA, 6, 7)

    print(a, na.print="-999")
```
- The output of the new vector is 1, 2, -999, 4, -999, 6, 7 this because of the code that i use earlier where the NA replace to -999.

## 15. A special type of function calls can appear on the left hand side of the assignment operator as in > class(x) <- "foo".

## follow the codes below:
```{r}
name = readline(prompt="Input your name: ")
  age = readline(prompt="Input your age: ")
  print(paste("My name is", name,"and I am",age,"years old."))
  print(R.version.string)
```
## What is the output of the above code?
- the output of the above code is "My name is Dave and I am 19 years old."
