---
title: "Rworksheet_cadiz#4b"
author: "John Dave R. Cadiz"
date: "2024-10-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## 1. Using the for loop, create an R script that will displat a 5x5 matrix as 
## shown in Figure 1. It must contain vectorA = [1,2,3,4,5] and a 5 x 5 zero 
## matrix.
```{r}
vectorA <- c(1,2,3,4,5)
 matrixfive <- matrix(0, nrow = 5, ncol = 5)
  for ( i in 1:5) {
    for (  j in 1:5) {
    matrixfive [i, j] <- vectorA[abs(i - j) + 1] - 1
    }
  }
 print(matrixfive)
```

## 2. Print the string "*" using for() function. The output should be the same 
## as shown in Figure.
```{r}
for ( i in 1:5) {
  for( j in 1:i) {
    cat("* ")
  }
  cat("\n")
}
```


## 3. Get an inpout from the user to print the Fibonacci sequence starting from
## the 1st input up to 500. Use repeat and break statements. Write the R scripts
## and its output
```{r}

```


## 4. Import the dataset as shown in Figure 1 you have created priviously.

## a. What us the R script for importing an excel or a csv file? Display the
## the first 6 rows of the dataset? Show your codes and its result.

## b. Create a subset for gender (female and male). How many observations are
## there in Male? How about in Female? Show your code and its results.

## 5. The monthly income of Dela Cruz family was spent on the following:

## a. Create a piechart that will include labels in percentage. Add some colors
## and title of the chart.. Write the R scripts and show its output.

## 6. Use the iris dataset.

data(iris)

## a. Check for the structure of the dataset using the str() function. Describe
## what you have seen in the output.

## b. Create an R object that will contain the mean of the sepal.length, sepal.
## width, petal.length, and petal.width. What is the R scripts and its result?

## c. Create a pie chart for the Species distribution. Add titles, legends, and
## colors. Write the R script and its result.

## d. Subset the species into setosa, versicolor, and virginica. Write the R
## scripts and  show the last six (6) rows of each species.

## e. Create a scatterplot of the sepal.length and sepal.width using the
## different species(setosa,versicolor, virginica). Add a title = "Iris Dataset,
## subtitle = "Sepal width and length, labels for the x and y axis, the pch 
## symbol and colors shoulds be based on the species.

## f. Interpret the result.



